### 2016-07-03 paper/extended-example.tex
added names
cleaning
added in %a
added in bib and end

BibEnd : Bib <=> End = ?
\end{lstlisting}

We are trying to synthesize \BibEndConv{}.

@@

After completing these necessary expansions, the problem becomes synthesizing a
lens between the regular expression
\begin{lstlisting}
BibTex'=("@inproceedings" | "@article" | "@book") "{" Word "," ("" | ("title={" Title "},")) ("" | ("author={" (Name", " Name (" " (Name | Initial))*) (" and " (Name", " Name (" " (Name | Initial))*))* "},"))
\end{lstlisting}
and
\begin{lstlisting}
EndNote'="%0 " ("Conference Paper" | "Journal Article" | "Book") "\n" ("%A " (Name (" " (Name | Initial))* (" " Name)) "\n")* ("" | ("%T " Title "\n")) "%1 " Word "\n"
\end{lstlisting}

>>>>

BibEnd : Bib <=> End = {
"author={Conway, John and Kleene, Stephen Cole}"
<-> "%A John Conway\n%A Stephen Cole Kleene" }
\end{lstlisting}

We are trying to synthesize \BibEnd{}.

@@

After completing these necessary expansions, the problem becomes synthesizing a
lens between the regular expression
\begin{lstlisting}
Bib: ""   | "author={" (" Name ", " Name (" " Name))* (" and " (" Name ", " Name (" " Name)))* "},"

End: ("%A " (Name (" " (Name))* " " Name) "\n")*
\end{lstlisting}
and
